\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-14 paper/experiments.tex
paper: fix unmerged file

\begin{table}
  \centerfloat
  \input{queries}
  \caption{The queries used in our experiments.}
  \label{fig:queries}
\end{table}

@@

Finally, we performed $CE-CART$ imputation on the entirety of the ACS table, in order to compare our system to the traditional, pre-processing approach to imputation.
We were unable to complete the full imputation due to resource constraints, but the process ran for more than one hour without terminating.
This time compares favorably to our maximum of \todo{add time}.
Given the varying needs of database users, \ProjectName{} clearly allows flexibility without a significant performance hit.

>>>>

\begin{table}
  \centerfloat
  \input{queries}
  \caption{Queries used in our experiments.}
  \label{fig:queries}
\end{table}

@@

Finally, we performed CE-CART imputation on the entirety of the ACS table, in order to compare our system to the traditional, pre-processing approach to imputation.
We were unable to complete the full imputation due to resource constraints, but the process ran for more than one hour without terminating.
This time compares favorably to our maximum of \todo{add time} for a query with imputation.
Given the varying needs of database users, \ProjectName{} clearly allows flexibility without a significant performance hit.
